Who Needs Privacy? Exploring the relationship between personality and need for privacy

### 2023-03-01 analyses.RmD
- major update - now set up as a registered report

---
title: "Who Needs Privacy? Exploring the relationship between personality and need for privacy"
subtitle: "Analyses"
output:
  html_document:
    toc: TRUE
    toc_float:
      collapsed: FALSE
    toc_depth: 2
    code_folding: hide
bibliography      : 
  - "bibliography/r-references.bib"
  - "bibliography/references.bib"
  # pdf_document:
  #   toc: TRUE
---

@@

```{r r-setup, include=F}
# install packages
# devtools::install_github("https://github.com/tdienlin/td")

@@

```{r data-wrangling}
d <- read_spss("data/Need+for+Privacy_August+16%2C+2021_15.33.sav")

# define vars and labels
vars_pers_fac <- c("HEX_HOH_SIN", "HEX_HOH_FAI", "HEX_HOH_GRE", "HEX_HOH_MOD", 
                   "HEX_EMO_FEA", "HEX_EMO_ANX", "HEX_EMO_DEP", "HEX_EMO_SEN", 
                   "HEX_EXT_SSE", "HEX_EXT_BOL", "HEX_EXT_SOC", "HEX_EXT_LIV", 
                   "HEX_AGR_FOR", "HEX_AGR_GEN", "HEX_AGR_FLX", "HEX_AGR_PAT", 
                   "HEX_CNS_ORG", "HEX_CNS_DIL", "HEX_CNS_PER", "HEX_CNS_PRU", 
                   "HEX_OPN_AES", "HEX_OPN_INQ", "HEX_OPN_CRE", "HEX_OPN_UNC", 
                   "HEX_ALT")
vars_pers_fac_txt <- c("Sincerity", "Fairness", "Greed avoidance", "Modesty", 
                       "Fearfulness", "Anxiety", "Dependence", "Sentimentality", 
                       "Social Self-Esteem", "Social Boldness", "Sociability", "Liveliness",
                       "Forgiveness", "Gentleness", "Flexibility", "Patience", 
                       "Organization", "Diligence", "Perfectionism", "Prudence", 
                       "Aesthetic Appreciation", "Inquisitiveness", "Creativeness", "Unconventionality", 
                       "Altruism")

@@

vars_pri <- c("NFP_INF", "NFP_PSY", "NFP_PHY", "NFP_CNC", "NFP_SPA", 
              "NFP_GOV", "NFP_INT", "NFP_ANO", "NFP_COM", "NFP_GEN")
vars_pri_txt <- c("Informational", "Psychological", "Physical", "Concealment", "Personal Space", 
                  "Government", "Interpersonal", "Anonymity", "Companies", "General")

vars_ses <- c("age", "gender", "ethnicity", "relationship", "college", "income", "conservatism")

```

@@

#### Dependence
 - When I suffer from a painful experience, I need someone to make me feel comfortable.
 - I can handle difficult situations without needing emotional support from anyone else.
 - Whenever I feel worried about something, I want to share my concern with another person.
 - I rarely discuss my problems with other people.

@@

## Need for privacy
### Informational

 - I would prefer that little is known about me. 
 - In general, I prefer to remain incognito. 
 - I don’t want my personal data to be publicly accessible. 
 - Not everyone has to know everything about me.

@@

### Psychological

 - I don’t like to talk about personal issues unless others do it first.
 - There are a lot of things about me that I don’t like to talk about with others. 
 - I feel uncomfortable when others tell me private things about their lives. 
 - It is hard for me to talk about my feelings and inner thoughts.

### Physiological

 - I don’t like it when strangers come too close to me. 
 - I feel uncomfortable when others enter my flat or room unannounced. 
 - I don’t like to stand in a dense crowd of people. 
 - I don’t like to sit next to a stranger on the tram or bus.

### Privacy from other People

 - My need for privacy is so strong that it prevents me from using social media actively. 
 - I don’t feel I need to tell my friends all my secrets.
 - I feel I need to protect my privacy from other people.
 - I prefer it when others don’t know much about me.

```{r}
model <- "NFP_INT =~ NFP_INT_01 + NFP_INT_02 + NFP_INT_03 + NFP_INT_04"
```

#### Validation

 - I need government agencies to respect my privacy, even if that makes catching criminals harder.,
 - I don’t want the government to gather data about me, even if that makes it harder to spend tax income efficiently.,
 - I don’t want government agencies to monitor my communication, even if that prevents terrorist attacks.,
 - I feel I need to protect my privacy from government agencies.

#### Validation

@@

 - I need to be able to use a fake account on social network sites to preserve my privacy. 
 - I feel I need to avoid places with video surveillance.
 - I prefer not to carry my drivers license or ID with me all the time to preserve my privacy.
 - I need to be able to surf the Internet anonymously. (new)

@@

#### Validation

 - I’m willing to pay more for products or services so that companies don’t have to sell my data.
 - I’m happy to give up a little bit of privacy, so that I can use certain apps or services for free.
 - I don’t want companies to gather information about me, even if that reduces the quality of their services.
 - I feel I need to protect my privacy from companies.

#### Validation

@@

 - I need a lot of privacy.
 - Privacy is very important to me.
 - I think a lot about how I can protect my privacy.
 - I need a lot of time for myself.

@@

#### Validation

@@

# a priori power analyses
pwr.r.test(r = sesoi, sig.level = .05, power = .95) ## too expensive
power_n_95 <- pwr.r.test(r = sesoi, sig.level = .05, power = .95)$n
```

A 5% error rate would imply collecting 1.293 participants, which was outside of our budget.

```{r}
pwr.r.test(r = sesoi, sig.level = .1, power = .9)
power_n_90 <- pwr.r.test(r = sesoi, sig.level = .1, power = .9)$n
```

A 10% error rate would imply collecting 853 participants, which was within our budget.

# Results
## Facets

```{r}
model_fac <- "
HEX_HOH_SIN =~ HEX_HOH_SIN_01 + HEX_HOH_SIN_02 + HEX_HOH_SIN_03 + HEX_HOH_SIN_04
HEX_HOH_FAI =~ HEX_HOH_FAI_01 + HEX_HOH_FAI_02 + HEX_HOH_FAI_03 + HEX_HOH_FAI_04
HEX_HOH_GRE =~ HEX_HOH_GRE_01 + HEX_HOH_GRE_02 + HEX_HOH_GRE_03 + HEX_HOH_GRE_04
HEX_HOH_MOD =~ HEX_HOH_MOD_01 + HEX_HOH_MOD_02 + HEX_HOH_MOD_03 + HEX_HOH_MOD_04
HEX_EMO_FEA =~ HEX_EMO_FEA_01 + HEX_EMO_FEA_02 + HEX_EMO_FEA_03 + HEX_EMO_FEA_04
HEX_EMO_ANX =~ HEX_EMO_ANX_01 + HEX_EMO_ANX_02 + HEX_EMO_ANX_03 + HEX_EMO_ANX_04
HEX_EMO_DEP =~ HEX_EMO_DEP_01 + HEX_EMO_DEP_02 + HEX_EMO_DEP_03 + HEX_EMO_DEP_04
HEX_EMO_SEN =~ HEX_EMO_SEN_01 + HEX_EMO_SEN_02 + HEX_EMO_SEN_03 + HEX_EMO_SEN_04
HEX_EXT_SSE =~ HEX_EXT_SSE_01 + HEX_EXT_SSE_02 + HEX_EXT_SSE_03 + HEX_EXT_SSE_04
HEX_EXT_BOL =~ HEX_EXT_BOL_01 + HEX_EXT_BOL_02 + HEX_EXT_BOL_03 + HEX_EXT_BOL_04
HEX_EXT_SOC =~ HEX_EXT_SOC_01 + HEX_EXT_SOC_02 + HEX_EXT_SOC_03 + HEX_EXT_SOC_04
HEX_EXT_LIV =~ HEX_EXT_LIV_01 + HEX_EXT_LIV_02 + HEX_EXT_LIV_03 + HEX_EXT_LIV_04
HEX_AGR_FOR =~ HEX_AGR_FOR_01 + HEX_AGR_FOR_02 + HEX_AGR_FOR_03 + HEX_AGR_FOR_04
HEX_AGR_GEN =~ HEX_AGR_GEN_01 + HEX_AGR_GEN_02 + HEX_AGR_GEN_03 + HEX_AGR_GEN_04
HEX_AGR_FLX =~ HEX_AGR_FLX_01 + HEX_AGR_FLX_02 + HEX_AGR_FLX_03 + HEX_AGR_FLX_04
HEX_AGR_PAT =~ HEX_AGR_PAT_01 + HEX_AGR_PAT_02 + HEX_AGR_PAT_03 + HEX_AGR_PAT_04
HEX_CNS_ORG =~ HEX_CNS_ORG_01 + HEX_CNS_ORG_02 + HEX_CNS_ORG_03 + HEX_CNS_ORG_04
HEX_CNS_DIL =~ HEX_CNS_DIL_01 + HEX_CNS_DIL_02 + HEX_CNS_DIL_03 + HEX_CNS_DIL_04
HEX_CNS_PER =~ HEX_CNS_PER_01 + HEX_CNS_PER_02 + HEX_CNS_PER_03 + HEX_CNS_PER_04
HEX_CNS_PRU =~ HEX_CNS_PRU_01 + HEX_CNS_PRU_02 + HEX_CNS_PRU_03 + HEX_CNS_PRU_04
HEX_OPN_AES =~ HEX_OPN_AES_01 + HEX_OPN_AES_02 + HEX_OPN_AES_03 + HEX_OPN_AES_04
HEX_OPN_INQ =~ HEX_OPN_INQ_01 + HEX_OPN_INQ_02 + HEX_OPN_INQ_03 + HEX_OPN_INQ_04
HEX_OPN_CRE =~ HEX_OPN_CRE_01 + HEX_OPN_CRE_02 + HEX_OPN_CRE_03 + HEX_OPN_CRE_04
HEX_OPN_UNC =~ HEX_OPN_UNC_01 + HEX_OPN_UNC_02 + HEX_OPN_UNC_03 + HEX_OPN_UNC_04
HEX_ALT =~ HEX_ALT_01 + HEX_ALT_02 + HEX_ALT_03 + HEX_ALT_04
NFP_INF =~ NFP_INF_01 + NFP_INF_02 + NFP_INF_03 + NFP_INF_04
NFP_PSY =~ NFP_PSY_01 + NFP_PSY_02 + NFP_PSY_03 + NFP_PSY_04
NFP_PHY =~ NFP_PHY_01 + NFP_PHY_02 + NFP_PHY_03 + NFP_PHY_04
NFP_CNC =~ NFP_CNC_01 + NFP_CNC_02 + NFP_CNC_03 + NFP_CNC_04
NFP_SPA =~ NFP_SPA_01 + NFP_SPA_02 + NFP_SPA_03 + NFP_SPA_04
NFP_GOV =~ NFP_GOV_01 + NFP_GOV_02 + NFP_GOV_03 + NFP_GOV_04
NFP_INT =~ NFP_INT_01 + NFP_INT_02 + NFP_INT_03 + NFP_INT_04
NFP_ANO =~ NFP_ANO_01 + NFP_ANO_02 + NFP_ANO_03 + NFP_ANO_04
NFP_COM =~ NFP_COM_01 + NFP_COM_02 + NFP_COM_03 + NFP_COM_04
NFP_GEN =~ NFP_GEN_01 + NFP_GEN_02 + NFP_GEN_03 + NFP_GEN_04
age =~ AGE
gender =~ GEN
ethnicity =~ ETH
relationship =~ REL_
college =~ COL_
income =~ INC
conservatism =~ CON
"
fit_fac <- sem(model_fac, d, estimator = "ML", fixed.x = TRUE)
summary(fit_fac, standardized = TRUE)

d_fac <- 
  standardizedsolution(fit_fac, ci = TRUE, level = .90) %>% 
  as.data.frame() %>% 
  filter(op == "~~", lhs %in% vars_pers_dim, rhs %in% vars_pri)

fig_fac <- ggplot(d_fac, aes(x = est.std, y = lhs)) +
  geom_point() +
  geom_errorbarh(aes(xmin = ci.lower, xmax = ci.upper)) +
  facet_wrap(vars(rhs), nrow = 1)

# tab_results <- data.frame(
#   tab_results_raw[1 : length(vars_pers_fac), ]$std.all,
#   tab_results_raw[(1 * length(vars_pers_fac) + 1) : (length(vars_pers_fac) * 2), ]$std.all,
#   tab_results_raw[(2 * length(vars_pers_fac) + 1) : (length(vars_pers_fac) * 3), ]$std.all,
#   tab_results_raw[(3 * length(vars_pers_fac) + 1) : (length(vars_pers_fac) * 4), ]$std.all,
#   tab_results_raw[(4 * length(vars_pers_fac) + 1) : (length(vars_pers_fac) * 5), ]$std.all,
#   tab_results_raw[(5 * length(vars_pers_fac) + 1) : (length(vars_pers_fac) * 6), ]$std.all,
#   tab_results_raw[(6 * length(vars_pers_fac) + 1) : (length(vars_pers_fac) * 7), ]$std.all,
#   tab_results_raw[(7 * length(vars_pers_fac) + 1) : (length(vars_pers_fac) * 8), ]$std.all,
#   tab_results_raw[(8 * length(vars_pers_fac) + 1) : (length(vars_pers_fac) * 9), ]$std.all,
#   tab_results_raw[(9 * length(vars_pers_fac) + 1) : (length(vars_pers_fac) * 10), ]$std.all
# )
# names(tab_results) <- vars_pri
# rownames(tab_results) <- vars_pers_fac
```

## Factors

@@

```{r}
model_dim <- "
HEX_HOH =~ HEX_HOH_SIN + HEX_HOH_FAI + HEX_HOH_GRE + HEX_HOH_MOD
HEX_HOH_SIN =~ HEX_HOH_SIN_01 + HEX_HOH_SIN_02 + HEX_HOH_SIN_03 + HEX_HOH_SIN_04
HEX_HOH_FAI =~ HEX_HOH_FAI_01 + HEX_HOH_FAI_02 + HEX_HOH_FAI_03 + HEX_HOH_FAI_04
HEX_HOH_GRE =~ HEX_HOH_GRE_01 + HEX_HOH_GRE_02 + HEX_HOH_GRE_03 + HEX_HOH_GRE_04
HEX_HOH_MOD =~ HEX_HOH_MOD_01 + HEX_HOH_MOD_02 + HEX_HOH_MOD_03 + HEX_HOH_MOD_04

@@

NFP_INF =~ NFP_INF_01 + NFP_INF_02 + NFP_INF_03 + NFP_INF_04
NFP_PSY =~ NFP_PSY_01 + NFP_PSY_02 + NFP_PSY_03 + NFP_PSY_04
NFP_PHY =~ NFP_PHY_01 + NFP_PHY_02 + NFP_PHY_03 + NFP_PHY_04
NFP_CNC =~ NFP_CNC_01 + NFP_CNC_02 + NFP_CNC_03 + NFP_CNC_04
NFP_SPA =~ NFP_SPA_01 + NFP_SPA_02 + NFP_SPA_03 + NFP_SPA_04
NFP_GOV =~ NFP_GOV_01 + NFP_GOV_02 + NFP_GOV_03 + NFP_GOV_04
NFP_INT =~ NFP_INT_01 + NFP_INT_02 + NFP_INT_03 + NFP_INT_04
NFP_ANO =~ NFP_ANO_01 + NFP_ANO_02 + NFP_ANO_03 + NFP_ANO_04
NFP_COM =~ NFP_COM_01 + NFP_COM_02 + NFP_COM_03 + NFP_COM_04
NFP_GEN =~ NFP_GEN_01 + NFP_GEN_02 + NFP_GEN_03 + NFP_GEN_04
"
fit_dim <- sem(model_dim, d, estimator = "ML", fixed.x = TRUE)
summary(fit_dim, standardized = TRUE)

# extract results
d_dim <- 
  standardizedsolution(fit_dim, ci = TRUE, level = .90) %>% 
  as.data.frame() %>% 
  filter(op == "~~", lhs %in% vars_pers_dim, rhs %in% vars_pri)

fig_dim <- ggplot(d_dim, aes(x = est.std, y = lhs)) +
  geom_point() +
  geom_errorbarh(aes(xmin = ci.lower, xmax = ci.upper)) +
  facet_wrap(vars(rhs), nrow = 1)

# tab_results <- data.frame(
#   tab_results_raw[1 : length(vars_pers_dim), ]$std.all,
#   tab_results_raw[(1 * length(vars_pers_dim) + 1) : (length(vars_pers_dim) * 2), ]$std.all,
#   tab_results_raw[(2 * length(vars_pers_dim) + 1) : (length(vars_pers_dim) * 3), ]$std.all,
#   tab_results_raw[(3 * length(vars_pers_dim) + 1) : (length(vars_pers_dim) * 4), ]$std.all,
#   tab_results_raw[(4 * length(vars_pers_dim) + 1) : (length(vars_pers_dim) * 5), ]$std.all,
#   tab_results_raw[(5 * length(vars_pers_dim) + 1) : (length(vars_pers_dim) * 6), ]$std.all,
#   tab_results_raw[(6 * length(vars_pers_dim) + 1) : (length(vars_pers_dim) * 7), ]$std.all,
#   tab_results_raw[(7 * length(vars_pers_dim) + 1) : (length(vars_pers_dim) * 8), ]$std.all,
#   tab_results_raw[(8 * length(vars_pers_dim) + 1) : (length(vars_pers_dim) * 9), ]$std.all,
#   tab_results_raw[(9 * length(vars_pers_dim) + 1) : (length(vars_pers_dim) * 10), ]$std.all
# )
# names(tab_results) <- vars_pri
# rownames(tab_results) <- vars_pers_dim
```

## SES

```{r}
model_ses <- "
age =~ AGE
gender =~ GEN
ethnicity =~ ETH
relationship =~ REL_
college =~ COL_
income =~ INC
conservatism =~ CON
NFP_INF =~ NFP_INF_01 + NFP_INF_02 + NFP_INF_03 + NFP_INF_04
NFP_PSY =~ NFP_PSY_01 + NFP_PSY_02 + NFP_PSY_03 + NFP_PSY_04
NFP_PHY =~ NFP_PHY_01 + NFP_PHY_02 + NFP_PHY_03 + NFP_PHY_04
NFP_CNC =~ NFP_CNC_01 + NFP_CNC_02 + NFP_CNC_03 + NFP_CNC_04
NFP_SPA =~ NFP_SPA_01 + NFP_SPA_02 + NFP_SPA_03 + NFP_SPA_04
NFP_GOV =~ NFP_GOV_01 + NFP_GOV_02 + NFP_GOV_03 + NFP_GOV_04
NFP_INT =~ NFP_INT_01 + NFP_INT_02 + NFP_INT_03 + NFP_INT_04
NFP_ANO =~ NFP_ANO_01 + NFP_ANO_02 + NFP_ANO_03 + NFP_ANO_04
NFP_COM =~ NFP_COM_01 + NFP_COM_02 + NFP_COM_03 + NFP_COM_04
NFP_GEN =~ NFP_GEN_01 + NFP_GEN_02 + NFP_GEN_03 + NFP_GEN_04
"
fit_ses <- sem(model_ses, d, estimator = "ML", fixed.x = TRUE)
summary(fit_ses, standardized = TRUE)

# extract results
d_ses <- 
  standardizedsolution(fit_ses, ci = TRUE, level = .90) %>% 
  as.data.frame() %>% 
  filter(op == "~~", lhs %in% vars_ses, rhs %in% vars_pri)

fig_ses <- ggplot(d_ses, aes(x = est.std, y = lhs)) +
  geom_point() +
  geom_errorbarh(aes(xmin = ci.lower, xmax = ci.upper)) +
  facet_wrap(vars(rhs), nrow = 1)

# tab_results <- data.frame(
#   tab_results_raw[1 : length(vars_ses), ]$std.all,
#   tab_results_raw[(1 * length(vars_ses) + 1) : (length(vars_ses) * 2), ]$std.all,
#   tab_results_raw[(2 * length(vars_ses) + 1) : (length(vars_ses) * 3), ]$std.all,
#   tab_results_raw[(3 * length(vars_ses) + 1) : (length(vars_ses) * 4), ]$std.all,
#   tab_results_raw[(4 * length(vars_ses) + 1) : (length(vars_ses) * 5), ]$std.all,
#   tab_results_raw[(5 * length(vars_ses) + 1) : (length(vars_ses) * 6), ]$std.all,
#   tab_results_raw[(6 * length(vars_ses) + 1) : (length(vars_ses) * 7), ]$std.all,
#   tab_results_raw[(7 * length(vars_ses) + 1) : (length(vars_ses) * 8), ]$std.all,
#   tab_results_raw[(8 * length(vars_ses) + 1) : (length(vars_ses) * 9), ]$std.all,
#   tab_results_raw[(9 * length(vars_ses) + 1) : (length(vars_ses) * 10), ]$std.all
# )
# names(tab_results) <- vars_pri
# rownames(tab_results) <- vars_ses
```

```{r}
save.image("data/workspace.RData")
```

>>>>

---
title: "Who Needs Privacy? Exploring the relationship between personality and need for privacy"
subtitle: "Analyses"
output:
  html_document:
    toc: TRUE
    toc_float:
      collapsed: FALSE
    toc_depth: 2
    code_folding: hide
    df_print: paged
bibliography      : 
  - "bibliography/r-references.bib"
  - "bibliography/references.bib"
  # pdf_document:
  #   toc: TRUE
---

@@

Here you can find the results of our study.

- At this point, we haven't yet collected data. 
- The results below use simulated data. 
- The data are random and don't make sense, but help to illustrate the overall approach and planned analyses.
- We'll later conduct additional analyses, for example model-alterations given misfit.

# Set-Up

```{r r-setup, include=T, echo=F}
# install packages
# devtools::install_github("https://github.com/tdienlin/td")

@@

```{r data-wrangling}
d <- read_spss("data/Need+for+Privacy_February+27%2C+2023_13.45.sav")
d <- rename(d, COL = COL_, REL = REL_)

# define vars and labels
vars_pers_fac <- c("HEX_HOH_SIN", "HEX_HOH_FAI", "HEX_HOH_GRE", "HEX_HOH_MOD", 
                   "HEX_EMO_FEA", "HEX_EMO_ANX", "HEX_EMO_DEP", "HEX_EMO_SEN", 
                   "HEX_EXT_SSE", "HEX_EXT_BOL", "HEX_EXT_SOC", "HEX_EXT_LIV", 
                   "HEX_AGR_FOR", "HEX_AGR_GEN", "HEX_AGR_FLX", "HEX_AGR_PAT", 
                   "HEX_CNS_ORG", "HEX_CNS_DIL", "HEX_CNS_PER", "HEX_CNS_PRU", 
                   "HEX_OPN_AES", "HEX_OPN_INQ", "HEX_OPN_CRE", "HEX_OPN_UNC", 
                   "HEX_ALT")
vars_pers_fac_txt <- c("Sincerity", "Fairness", "Greed avoidance", "Modesty", 
                       "Fearfulness", "Anxiety", "Dependence", "Sentimentality", 
                       "Social self-esteem", "Social boldness", "Sociability", "Liveliness",
                       "Forgiveness", "Gentleness", "Flexibility", "Patience", 
                       "Organization", "Diligence", "Perfectionism", "Prudence", 
                       "Aesthetic appreciation", "Inquisitiveness", "Creativeness", "Unconventionality", 
                       "Altruism")

@@

vars_pri <- c("NFP_SOC", "NFP_PHY", "NFP_PSY",
              "NFP_GOV", "NFP_COM", 
              "NFP_INF", "NFP_ANO", "NFP_GEN")
vars_pri_txt <- c("Social", "Physical", "Psychological",
                  "Companies", "Governnment",
                  "Anonynmity", "Infornmational", "General")
vars_pri_txt_brk <- c("Social", "Physical", "Psycho-\nlogical",
                  "Companies", "Govern-\nment",
                  "Anony-\nmity", "Infor-\nmational", "General")
vars_pri_txt_abr <- c("Social", "Phys.", "Psych.",
                  "Comp.", "Gov.",
                  "Anonym.", "Inform.", "General")

vars_ses <- c("AGE", "GEN", "ETH", "REL", "COL", "INC", "CON")
vars_ses_txt <- c("Age", "Gender", "Ethnicity", "Relationship", "College", "Income", "Conservatism")
```

@@

#### Dependence

 - When I suffer from a painful experience, I need someone to make me feel comfortable.
 - I can handle difficult situations without needing emotional support from anyone else.
 - Whenever I feel worried about something, I want to share my concern with another person.
 - I rarely discuss my problems with other people.

@@

## Need for privacy
### Psychological

 1.	I don’t like to talk about personal issues with others unless they do it first.
 2.	There are a lot of things about me that I don’t like to talk about with others.
 3.	I prefer not to share my feelings and inner thoughts with others.
 4.	I don't like it when others talk to me about their private issues.

### Physical

 1.	I don’t like it when strangers come too close to me.
 2.	I don’t like to stand in a dense crowd of people.
 3.	I don’t like to sit next to a stranger on a tram, bus, or plane.
 4.	I hate it when people enter my personal space uninvited.

### Social

 1.	I don’t feel comfortable interacting with other people.
 2.	I often want to be alone.
 3.	I’m a fairly anti-social person.
 4.	I prefer to work independently in most situations.

```{r}
model <- "NFP_SOC =~ NFP_SOC_01 + NFP_SOC_02 + NFP_SOC_03 + NFP_SOC_04"
```

 1.	I need government agencies to respect my privacy, even if that makes catching criminals harder.
 2.	I don’t want the government to gather data about me, even if that makes it harder to spend tax income effectively.
 3.	I don’t want government agencies to monitor my communication, even if that stops terrorist attacks.
 4.	I feel I need to protect my privacy from government agencies.

 1. I’m willing to pay more for products or services so that companies don’t have to sell my data.
 2. I’m happy to give up a little bit of privacy so that I can use certain apps or services for free.
 3. I don’t want companies to collect data about me, even if that makes their services worse.
 4. I feel I need to protect my privacy from companies.

### Informational

 1.	I would prefer that little is known about me.
 2.	I don’t want my personal data to be publicly accessible.
 3.	It is important to me that records pertaining to me remain confidential.
 4.	I prefer that others cannot easily find information about me on the Internet.

@@

@@

 1.	I would prefer to use a fake account on social network sites to preserve my privacy.
 2.	I feel I need to avoid places with video surveillance.
 3.	I prefer not to carry my driver’s license or ID with me all the time to preserve my privacy.
 4.	I need to be able to surf the Internet anonymously.

@@

@@

 1.	I need a lot of privacy.
 2.	Privacy is very important to me.
 3.	I think a lot about how I can protect my privacy.
 4.	I value privacy a lot.

@@

@@

# a priori power analyses
pwr.r.test(r = sesoi, sig.level = .05, power = .95)
power_n_95 <- pwr.r.test(r = sesoi, sig.level = .05, power = .95)$n
```

A 5% error rate would imply collecting 1.293 participants.

# Results
## SES

```{r}
model_ses <- "
# SES
Age =~ AGE
Gender =~ GEN
Ethnicity =~ ETH
Relationship =~ REL
College =~ COL
Income =~ INC
Conservatism =~ CON

# Privacy
NFP_PHY =~ NFP_PHY_01 + NFP_PHY_02 + NFP_PHY_03 + NFP_PHY_04
NFP_PSY =~ NFP_PSY_01 + NFP_PSY_02 + NFP_PSY_03 + NFP_PSY_04
NFP_SOC =~ NFP_SOC_01 + NFP_SOC_02 + NFP_SOC_03 + NFP_SOC_04
NFP_COM =~ NFP_COM_01 + NFP_COM_02 + NFP_COM_03 + NFP_COM_04
NFP_GOV =~ NFP_GOV_01 + NFP_GOV_02 + NFP_GOV_03 + NFP_GOV_04
NFP_ANO =~ NFP_ANO_01 + NFP_ANO_02 + NFP_ANO_03 + NFP_ANO_04
NFP_INF =~ NFP_INF_01 + NFP_INF_02 + NFP_INF_03 + NFP_INF_04
NFP_GEN =~ NFP_GEN_01 + NFP_GEN_02 + NFP_GEN_03 + NFP_GEN_04
"
fit_ses <- sem(model_ses, d, estimator = "ML", fixed.x = TRUE)
summary(fit_ses, standardized = TRUE)

# get standardized data
d_ses <- 
  standardizedsolution(fit_ses)
```

```{r}
# make table
tab_ses <- 
  d_ses %>% 
  as.data.frame() %>% 
  filter(op == "~~", lhs %in% vars_ses_txt, rhs %in% vars_pri) %>% 
  select("Sociodemographics" = lhs, "Need for privacy" = rhs, est.std) %>% 
  mutate(`Need for privacy` = factor(`Need for privacy`, levels = vars_pri, labels = vars_pri_txt)) %>% 
  pivot_wider(id_cols = "Sociodemographics", names_from = "Need for privacy", values_from = "est.std") %>% 
  as.data.frame()
tab_ses
```

## Dimensions

@@

```{r}
model_dim <- "
# Personality Factors
HEX_HOH =~ HEX_HOH_SIN + HEX_HOH_FAI + HEX_HOH_GRE + HEX_HOH_MOD
HEX_HOH_SIN =~ HEX_HOH_SIN_01 + HEX_HOH_SIN_02 + HEX_HOH_SIN_03 + HEX_HOH_SIN_04
HEX_HOH_FAI =~ HEX_HOH_FAI_01 + HEX_HOH_FAI_02 + HEX_HOH_FAI_03 + HEX_HOH_FAI_04
HEX_HOH_GRE =~ HEX_HOH_GRE_01 + HEX_HOH_GRE_02 + HEX_HOH_GRE_03 + HEX_HOH_GRE_04
HEX_HOH_MOD =~ HEX_HOH_MOD_01 + HEX_HOH_MOD_02 + HEX_HOH_MOD_03 + HEX_HOH_MOD_04

@@

# Privacy
NFP_PHY =~ NFP_PHY_01 + NFP_PHY_02 + NFP_PHY_03 + NFP_PHY_04
NFP_PSY =~ NFP_PSY_01 + NFP_PSY_02 + NFP_PSY_03 + NFP_PSY_04
NFP_SOC =~ NFP_SOC_01 + NFP_SOC_02 + NFP_SOC_03 + NFP_SOC_04
NFP_COM =~ NFP_COM_01 + NFP_COM_02 + NFP_COM_03 + NFP_COM_04
NFP_GOV =~ NFP_GOV_01 + NFP_GOV_02 + NFP_GOV_03 + NFP_GOV_04
NFP_ANO =~ NFP_ANO_01 + NFP_ANO_02 + NFP_ANO_03 + NFP_ANO_04
NFP_INF =~ NFP_INF_01 + NFP_INF_02 + NFP_INF_03 + NFP_INF_04
NFP_GEN =~ NFP_GEN_01 + NFP_GEN_02 + NFP_GEN_03 + NFP_GEN_04
"
fit_dim <- sem(model_dim, d, estimator = "ML", fixed.x = TRUE)
summary(fit_dim, standardized = TRUE)

# get standardized data
d_dim <- 
  standardizedsolution(fit_dim)
```

```{r}
# make table
tab_dim <- 
  d_dim %>% 
  as.data.frame() %>% 
  filter(op == "~~", lhs %in% vars_pers_dim, rhs %in% vars_pri) %>% 
  select("Personality dimension" = lhs, "Need for privacy" = rhs, est.std) %>% 
  mutate(`Need for privacy` = factor(`Need for privacy`, levels = vars_pri, labels = vars_pri_txt)) %>% 
  pivot_wider(id_cols = "Personality dimension", names_from = "Need for privacy", values_from = "est.std") %>% 
  mutate(`Personality dimension` = factor(`Personality dimension`, levels = vars_pers_dim, labels = vars_pers_dim_txt)) %>% 
  as.data.frame()
tab_dim
```

## Facets

```{r}
model_fac <- "
# Personality
HEX_HOH_SIN =~ HEX_HOH_SIN_01 + HEX_HOH_SIN_02 + HEX_HOH_SIN_03 + HEX_HOH_SIN_04
HEX_HOH_FAI =~ HEX_HOH_FAI_01 + HEX_HOH_FAI_02 + HEX_HOH_FAI_03 + HEX_HOH_FAI_04
HEX_HOH_GRE =~ HEX_HOH_GRE_01 + HEX_HOH_GRE_02 + HEX_HOH_GRE_03 + HEX_HOH_GRE_04
HEX_HOH_MOD =~ HEX_HOH_MOD_01 + HEX_HOH_MOD_02 + HEX_HOH_MOD_03 + HEX_HOH_MOD_04
HEX_EMO_FEA =~ HEX_EMO_FEA_01 + HEX_EMO_FEA_02 + HEX_EMO_FEA_03 + HEX_EMO_FEA_04
HEX_EMO_ANX =~ HEX_EMO_ANX_01 + HEX_EMO_ANX_02 + HEX_EMO_ANX_03 + HEX_EMO_ANX_04
HEX_EMO_DEP =~ HEX_EMO_DEP_01 + HEX_EMO_DEP_02 + HEX_EMO_DEP_03 + HEX_EMO_DEP_04
HEX_EMO_SEN =~ HEX_EMO_SEN_01 + HEX_EMO_SEN_02 + HEX_EMO_SEN_03 + HEX_EMO_SEN_04
HEX_EXT_SSE =~ HEX_EXT_SSE_01 + HEX_EXT_SSE_02 + HEX_EXT_SSE_03 + HEX_EXT_SSE_04
HEX_EXT_BOL =~ HEX_EXT_BOL_01 + HEX_EXT_BOL_02 + HEX_EXT_BOL_03 + HEX_EXT_BOL_04
HEX_EXT_SOC =~ HEX_EXT_SOC_01 + HEX_EXT_SOC_02 + HEX_EXT_SOC_03 + HEX_EXT_SOC_04
HEX_EXT_LIV =~ HEX_EXT_LIV_01 + HEX_EXT_LIV_02 + HEX_EXT_LIV_03 + HEX_EXT_LIV_04
HEX_AGR_FOR =~ HEX_AGR_FOR_01 + HEX_AGR_FOR_02 + HEX_AGR_FOR_03 + HEX_AGR_FOR_04
HEX_AGR_GEN =~ HEX_AGR_GEN_01 + HEX_AGR_GEN_02 + HEX_AGR_GEN_03 + HEX_AGR_GEN_04
HEX_AGR_FLX =~ HEX_AGR_FLX_01 + HEX_AGR_FLX_02 + HEX_AGR_FLX_03 + HEX_AGR_FLX_04
HEX_AGR_PAT =~ HEX_AGR_PAT_01 + HEX_AGR_PAT_02 + HEX_AGR_PAT_03 + HEX_AGR_PAT_04
HEX_CNS_ORG =~ HEX_CNS_ORG_01 + HEX_CNS_ORG_02 + HEX_CNS_ORG_03 + HEX_CNS_ORG_04
HEX_CNS_DIL =~ HEX_CNS_DIL_01 + HEX_CNS_DIL_02 + HEX_CNS_DIL_03 + HEX_CNS_DIL_04
HEX_CNS_PER =~ HEX_CNS_PER_01 + HEX_CNS_PER_02 + HEX_CNS_PER_03 + HEX_CNS_PER_04
HEX_CNS_PRU =~ HEX_CNS_PRU_01 + HEX_CNS_PRU_02 + HEX_CNS_PRU_03 + HEX_CNS_PRU_04
HEX_OPN_AES =~ HEX_OPN_AES_01 + HEX_OPN_AES_02 + HEX_OPN_AES_03 + HEX_OPN_AES_04
HEX_OPN_INQ =~ HEX_OPN_INQ_01 + HEX_OPN_INQ_02 + HEX_OPN_INQ_03 + HEX_OPN_INQ_04
HEX_OPN_CRE =~ HEX_OPN_CRE_01 + HEX_OPN_CRE_02 + HEX_OPN_CRE_03 + HEX_OPN_CRE_04
HEX_OPN_UNC =~ HEX_OPN_UNC_01 + HEX_OPN_UNC_02 + HEX_OPN_UNC_03 + HEX_OPN_UNC_04
HEX_ALT =~ HEX_ALT_01 + HEX_ALT_02 + HEX_ALT_03 + HEX_ALT_04
